### 2015-02-03 Manuscript/Missing_mammals-draft.tex
Draft init

\documentclass[a4paper,11pt]{article}

\usepackage{natbib}
\usepackage{enumerate}
\usepackage[osf]{mathpazo}
\usepackage{lastpage} 
\pagenumbering{arabic}
\linespread{1.66}

@@

\begin{flushright}
Version dated: \today
\end{flushright}
\begin{center}

%Title
\noindent{\Large{\bf{Missing living mammals}}}\\
\bigskip
%Author
\noindent{Thomas Guillerme - guillert@tcd.ie - http://tguillerme.github.io/}\\

\end{center}

@@

Google scholars
\textit{order} ("morphology" OR "morphological" OR "cladistic") AND characters matrix paleontology phylogeny
since 2010

\subsection{Mammalian orders terms}
The searched mammalian order terms are available in search_terms_latin.txt or search_terms_meta.txt. The file containing the meta names is the latin name files without the following suffixes: Mammal     @ia
Monothrem     @ata
Marsupial     @ia
Placental     @ia
Macroscelid     @ea
Afrosoricid     @a
Tubulident     @ata
Hyracoid     @ea
Proboscid     @ea
Siren     @ia
Pilos     @a
Cingul     @ata
Scandent     @ia
Dermopter     @a
Primat     @es
Lagomorph     @a
Rodent     @ia
Erinaceomorph     @a
Soricomorph     @a
Cetac     @ea
Artiodactyl     @a
Chiropter     @a
Perissodactyl     @a
Pholidot     @a
Carnivor     @a
Didelphimorph     @ia
Paucitubercul     @ata
Microbiother     @ia
Dasyuromorph     @ia
Peramelemorph     @ia
Notoryctemorph     @ia
Diprotodont     @ia
Monotrem     @ata

-Web of science

-Data bases???
Rose Mounce

-Tree base (through Dryad)
morpholog* OR combine*
mammal*
\textit{order}

-Morphobank
mammal*
\textit{order}

\bibliographystyle{sysbio} %don't write the suffix
\bibliography{References}

\end{document}

>>>>

%Authors guidlines: http://royalsocietypublishing.org/instructions-authors#question5

\documentclass[12pt,letterpaper]{article}

%Packages
\usepackage{pdflscape}
\usepackage{fixltx2e}
\usepackage{textcomp}
\usepackage{fullpage}
\usepackage{natbib}
\usepackage{float}
\usepackage{latexsym}
\usepackage{url}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{array}
\usepackage[version=3]{mhchem}
\usepackage{ifthen}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{amstext}
\usepackage{enumerate}
\usepackage[osf]{mathpazo}
\usepackage{dcolumn}
\usepackage{lineno}
\pagenumbering{arabic}

%Pagination style and stuff
\linespread{2}
\raggedright
\setlength{\parindent}{0.5in}
\setcounter{secnumdepth}{0} 
\renewcommand{\section}[1]{%
\bigskip
\begin{center}
\begin{Large}
\normalfont\scshape #1
\medskip
\end{Large}
\end{center}}
\renewcommand{\subsection}[1]{%
\bigskip
\begin{center}
\begin{large}
\normalfont\itshape #1
\end{large}
\end{center}}
\renewcommand{\subsubsection}[1]{%
\vspace{2ex}
\noindent
\textit{#1.}---}
\renewcommand{\tableofcontents}{}
\bibpunct{(}{)}{;}{a}{}{,}

%---------------------------------------------
%
%       START
%
%---------------------------------------------

@@

%Running head
\begin{flushright}
Version dated: \today
\end{flushright}
\bigskip
\noindent RH: Missing morphological data in living mammals

\bigskip
\medskip
\begin{center}

\noindent{\Large \bf Missing morphological data in living mammals}

\bigskip

\noindent {\normalsize \sc Thomas Guillerme$^1$$^,$$^2$$^*$, and Natalie Cooper$^1$$^,$$^2$}\\
\noindent {\small \it 
$^1$School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\
$^2$Trinity Centre for Biodiversity Research, Trinity College Dublin, Dublin 2, Ireland.}\\
\end{center}
\medskip
\noindent{*\bf Corresponding author.} \textit{Zoology Building, Trinity College Dublin, Dublin 2, Ireland; E-mail: guillert@tcd.ie; Fax: +353 1 6778094; Tel: +353 1 896 2571.}\\
\vspace{1in}

%Line numbering
\modulolinenumbers[1]
\linenumbers

%---------------------------------------------
%
%       ABSTRACT
%
%---------------------------------------------

\newpage
\begin{abstract}

\end{abstract}

\noindent ()\\

\vspace{1.5in}

\newpage

%---------------------------------------------
%
%       INTRODUCTION
%
%---------------------------------------------

\section{Introduction}

%---------------------------------------------
%
%       METHODS
%
%---------------------------------------------

\newpage

\section{Material and Methods}

@@

\subsection{Mammalian orders terms}
The searched mammalian order terms are available in search_terms_latin.txt or search_terms_meta.txt. The file containing the meta names is the Latin name files but with replacing the latin suffixes ([ia|ata|ea|a]) by a joker character (*) and by replacing the first letter by a upper/lower case meta character (e.g. [Aa]).

\subsubsection{Ross Mounce data set}
I selected all the matrices containing at least one of the mammalian orders names from Ross Mounce GitHub cladistic-data/nexus_files repository (accessed on the 02/12/2014).

\subsection{Graeme Lloyd}
Selecting the downloadable matrices

\subsection{Morphobank}
\textit{order}

\subsection{Google scholars}
20 first results since 2010 with the following key words:
\textit{order} ("morphology" OR "morphological" OR "cladistic") AND characters matrix paleontology phylogeny

\section{Wrong Bionmial names and typos}
I fixed the wrong bionomial names format (e.g. H. sapiens) into the correct ones (e.g. Homo sapiens) manually using the PaleoDB and http://www.helsinki.fi/~mhaaramo/metazoa/deuterostoma/chordata/synapsida/eutheria/artiodactyla/anthracotheriidae.html and the Wilson Reeder database.
I fixed typos and invalid characters in taxa names manually

%---------------------------------------------
%
%       RESULTS
%
%---------------------------------------------

\section{Results}

%---------------------------------------------
%
%       DISCUSSION
%
%---------------------------------------------

\section{Discussion}

%Biology letters various stuff
\section{Ethics statement}
\section{Data accessibility statement}
\section{Authors’ contributions statement}
\section{Acknowledgements}
\section{Funding statement}

%\bibliographystyle{}
%\bibliography{}

%Tables
%Figures

%END
\end{document}
